### 2022-06-27 draft.tex
Deploying to gh-pages from @ PoisotLab/ms_ncbitaxonomy_softwarenote@aa83c56a0a5fcc0340da9cffe96db0f5576f2c28 🚀

%
\href{https://orcid.org/0000-0002-0735-5184}{Timothée\,Poisot}%
%
\,\textsuperscript{1,2}\quad %
\href{https://orcid.org/0000-0002-0965-1649}{Rory\,Gibb}%
%
\,\textsuperscript{3,4}\quad %
\href{https://orcid.org/0000-0002-4308-6321}{Sadie J.\,Ryan}%
%
\,\textsuperscript{5,6,7}\quad %
\href{https://orcid.org/0000-0001-6960-8434}{Colin J.\,Carlson}%
%
\,\textsuperscript{8,9}

\textsuperscript{1}\,Université de Montréal, Départment de Sciences
Biologiques, Montréal QC, Canada\quad \textsuperscript{2}\,Québec Centre
for Biodiversity Science, Montréal, QC,
Canada\quad \textsuperscript{3}\,Centre on Climate Change and Planetary
Health, London School of Hygiene and Tropical Medicine, London,
UK\quad \textsuperscript{4}\,Centre for Mathematical Modelling of
Infectious Diseases, London School of Hygiene and Tropical Medicine,
London, UK\quad \textsuperscript{5}\,Emerging Pathogens Institute,
University of Florida, Gainesville, FL, United States of
America\quad \textsuperscript{6}\,School of Life Sciences, University of
KwaZulu-Natal, Durban, South Africa\quad \textsuperscript{7}\,Department
of Geography, University of Florida, Gainesville, FL, United States of
America\quad \textsuperscript{8}\,Department of Microbiology and
Immunology, Georgetown University Medical Center, Georgetown University,
Washington, D.C., United States of
America\quad \textsuperscript{9}\,Center for Global Health Science and
Security, Georgetown University Medical Center, Georgetown University,
Washington, D.C., United States of America

@@

Finally, taxonomic nomenclature changes regularly, with groups being
split, merged, or moved to a new position in the tree of life; this is,
notably, a common occurrence with viral taxonomy, each subsequent
version of which can differ markedly from the last; compare, \emph{e.g}
Lefkowitz et al. (2018) to Walker et al. (2020), where entire viral
sub-trees were split, re-organized, and created within just two years.
These taxonomic changes have profound implications for the way we
perceive biodiversity at global scales (Meier 2009), to the point were
taxonomic revisions should sometimes be actively conducted to improve
\emph{e.g.} conservation outcomes (Melville et al. 2021).

@@

@@

\leavevmode\hypertarget{ref-Meier2009BioRes}{}%
Meier, R. 2009. Biodiversity Research Based on Taxonomic Revisions - A
Tale of Unrealized Opportunities -. - In: pp. 323--345.

>>>>

%
\href{https://orcid.org/0000-0002-0735-5184}{Timothée\,Poisot}%
%
\,\textsuperscript{1,2}\quad %
\href{https://orcid.org/0000-0002-0965-1649}{Rory\,Gibb}%
%
\,\textsuperscript{3,4,5}\quad %
\href{https://orcid.org/0000-0002-4308-6321}{Sadie J.\,Ryan}%
%
\,\textsuperscript{6,7,8}\quad %
\href{https://orcid.org/0000-0001-6960-8434}{Colin J.\,Carlson}%
%
\,\textsuperscript{9,10}

\textsuperscript{1}\,Université de Montréal, Départment de Sciences
Biologiques, Montréal QC, Canada\quad \textsuperscript{2}\,Québec Centre
for Biodiversity Science, Montréal, QC,
Canada\quad \textsuperscript{3}\,Centre on Climate Change and Planetary
Health, London School of Hygiene and Tropical Medicine, London,
UK\quad \textsuperscript{4}\,Centre for Mathematical Modelling of
Infectious Diseases, London School of Hygiene and Tropical Medicine,
London, UK\quad \textsuperscript{5}\,Current address: Centre for
Biodiversity and Environment Research, University College London,
London, UK\quad \textsuperscript{6}\,Emerging Pathogens Institute,
University of Florida, Gainesville, FL, United States of
America\quad \textsuperscript{7}\,School of Life Sciences, University of
KwaZulu-Natal, Durban, South Africa\quad \textsuperscript{8}\,Department
of Geography, University of Florida, Gainesville, FL, United States of
America\quad \textsuperscript{9}\,Department of Microbiology and
Immunology, Georgetown University Medical Center, Georgetown University,
Washington, D.C., United States of
America\quad \textsuperscript{10}\,Center for Global Health Science and
Security, Georgetown University Medical Center, Georgetown University,
Washington, D.C., United States of America

@@

Finally, taxonomic nomenclature changes regularly, with groups being
split, merged, or moved to a new position in the tree of life; this is,
notably, a common occurrence with viral taxonomy, each subsequent
version of which can differ markedly from the last; compare, \emph{e.g}
Lefkowitz et al. (2018) to Walker et al. (2020), where entire viral
sub-trees were split, re-organized, and created within just two years.
These taxonomic changes have profound implications for the way we
perceive biodiversity at global scales (Dikow et al. 2009), to the point
were taxonomic revisions should sometimes be actively conducted to
improve \emph{e.g.} conservation outcomes (Melville et al. 2021).

@@

\leavevmode\hypertarget{ref-Dikow2009BioRes}{}%
Dikow, T. et al. 2009. Biodiversity Research Based on Taxonomic
Revisions - A Tale of Unrealized Opportunities. - In: Diptera Diversity:
Status, Challenges and Tools. Brill, pp. 323--346.

@@

### 2022-06-27 preprint.tex
Deploying to gh-pages from @ PoisotLab/ms_ncbitaxonomy_softwarenote@aa83c56a0a5fcc0340da9cffe96db0f5576f2c28 🚀

\medskip
\begin{flushleft}
{\small
%
\href{https://orcid.org/0000-0002-0735-5184}{Timothée\,Poisot}%
%
\,\textsuperscript{1,2}, %
\href{https://orcid.org/0000-0002-0965-1649}{Rory\,Gibb}%
%
\,\textsuperscript{3,4}, %
\href{https://orcid.org/0000-0002-4308-6321}{Sadie J.\,Ryan}%
%
\,\textsuperscript{5,6,7}, %
\href{https://orcid.org/0000-0001-6960-8434}{Colin J.\,Carlson}%
%
\,\textsuperscript{8,9}
\vskip 1em
\textsuperscript{1}\,Université de Montréal, Départment de Sciences
Biologiques, Montréal QC, Canada; \textsuperscript{2}\,Québec Centre for
Biodiversity Science, Montréal, QC, Canada; \textsuperscript{3}\,Centre
on Climate Change and Planetary Health, London School of Hygiene and
Tropical Medicine, London, UK; \textsuperscript{4}\,Centre for
Mathematical Modelling of Infectious Diseases, London School of Hygiene
and Tropical Medicine, London, UK; \textsuperscript{5}\,Emerging
Pathogens Institute, University of Florida, Gainesville, FL, United
States of America; \textsuperscript{6}\,School of Life Sciences,
University of KwaZulu-Natal, Durban, South
Africa; \textsuperscript{7}\,Department of Geography, University of
Florida, Gainesville, FL, United States of
America; \textsuperscript{8}\,Department of Microbiology and Immunology,
Georgetown University Medical Center, Georgetown University, Washington,
D.C., United States of America; \textsuperscript{9}\,Center for Global
Health Science and Security, Georgetown University Medical Center,
Georgetown University, Washington, D.C., United States of America\\
\vskip 1em
\textbf{Correspondance to:}\\
Timothée Poisot --- \texttt{timothee.poisot@umontreal.ca}\\
}
\end{flushleft}

>>>>

\medskip
\begin{flushleft}
{\small
%
\href{https://orcid.org/0000-0002-0735-5184}{Timothée\,Poisot}%
%
\,\textsuperscript{1,2}, %
\href{https://orcid.org/0000-0002-0965-1649}{Rory\,Gibb}%
%
\,\textsuperscript{3,4,5}, %
\href{https://orcid.org/0000-0002-4308-6321}{Sadie J.\,Ryan}%
%
\,\textsuperscript{6,7,8}, %
\href{https://orcid.org/0000-0001-6960-8434}{Colin J.\,Carlson}%
%
\,\textsuperscript{9,10}
\vskip 1em
\textsuperscript{1}\,Université de Montréal, Départment de Sciences
Biologiques, Montréal QC, Canada; \textsuperscript{2}\,Québec Centre for
Biodiversity Science, Montréal, QC, Canada; \textsuperscript{3}\,Centre
on Climate Change and Planetary Health, London School of Hygiene and
Tropical Medicine, London, UK; \textsuperscript{4}\,Centre for
Mathematical Modelling of Infectious Diseases, London School of Hygiene
and Tropical Medicine, London, UK; \textsuperscript{5}\,Current address:
Centre for Biodiversity and Environment Research, University College
London, London, UK; \textsuperscript{6}\,Emerging Pathogens Institute,
University of Florida, Gainesville, FL, United States of
America; \textsuperscript{7}\,School of Life Sciences, University of
KwaZulu-Natal, Durban, South Africa; \textsuperscript{8}\,Department of
Geography, University of Florida, Gainesville, FL, United States of
America; \textsuperscript{9}\,Department of Microbiology and Immunology,
Georgetown University Medical Center, Georgetown University, Washington,
D.C., United States of America; \textsuperscript{10}\,Center for Global
Health Science and Security, Georgetown University Medical Center,
Georgetown University, Washington, D.C., United States of America\\
\vskip 1em
\textbf{Correspondance to:}\\
Timothée Poisot --- \texttt{timothee.poisot@umontreal.ca}\\
}
\end{flushleft}
